---
title: "Reproducible Pitch Presentation: Resting Metabolic Calculator"
author: "Tran Bich Nguyen"
date: "8/11/2022"
output: slidy_presentation
---

##    Overview

Link to Application: 
https://tbn111.shinyapps.io/ShinyApplication/

The application above calculates the user's resting metabolic rate, which is the number of calories burned while at rest. 

Calculations are derived using the Mifflin-St Jeor Equation, which is ((10 * weight(kg)) + (6.25 * height(cm)) - (5 * age(years)) + 5) for men, and ((10 * weight(kg)) + (6.25 * height(cm)) - (5 * age(years)) - 161) for women, respectively. 

The user's resting metabolic rate is then multiplied by a factor ranging from 1.2 to 1.9 to account for the user's level of exercise.  


##    Calculations Pt. 1

###   Resting Metabolic Rate Calucation and Example
```{r resting metabolic rate, echo = TRUE}
 
# Resting Metabolic Rate Algorithm
   
    resting_metabolic_rate <- function(gender, age, height, weight) {
      if (gender == "Male")  {
      metabolic_rate <- round((10 * weight) + (6.25 * height) - (5 * age) + 5)}
      else {metabolic_rate <- round((10 * weight) + (6.25 * height) - (5 * age) - 161)}
      return(metabolic_rate)
    }
    

# Example

resting_metabolic_rate(gender = "Male", age = 50, height = 180, weight = 50)

```

##    Calculations Pt. 2

###   Resting Metabolic Rate Accounting for Level of Excercise Calculation and Example

```{r exercise, echo = TRUE}

#Resting Metabolic Rate Accounting for Level of Exercise Algorithm

    rate <- function(gender, age, weight, height, exercise)  {
      if (gender == "Male") {
        metabolic_rate <- round((10 * weight) + (6.25 * height) - (5 * age) + 5)}
      else {metabolic_rate <- round((10 * weight) + (6.25 * height) - (5 * age) - 161)}
      if (exercise == "Sedentary (little to no exercise)")  {exercise_rate <- round(metabolic_rate * 1.2)}
      else if (exercise == "Lightly active (exercise 1-3 days/week)") {exercise_rate <- round(metabolic_rate * 1.375)}
      else if (exercise == "Moderately active (exercise 3-5 days/week)")  {exercise_rate <- round(metabolic_rate * 1.55)}
      else if (exercise == "Active (exercise 6-7 days/week)") {exercise_rate <- round(metabolic_rate * 1.725)}
      else {exercise_rate <- round(metabolic_rate * 1.9)}
      return(exercise_rate)
    }


#Example

rate(gender = "Male", age = 50, height = 180, weight = 50, exercise = "Lightly active (exercise 1-3 days/week)")

```

##    Additional Resources

- Mifflin St-Jeor Equation:
https://pubmed.ncbi.nlm.nih.gov/15883556/

